---
title: "daily_activity"
author: "mglujoy"
date: "2023-09-15"
output: html_document
---
## Analyzing dailyActivity_merged.csv
### Loading Libraries
```{r loading libraries}
library(tidyverse)
library(here)
library(skimr)
library(janitor)
library(dplyr)
library(ggplot2)
library(ggpmisc)
library(quantreg)
```
### Loading CSV
```{r loading csv}
dailyActivity <- read_csv("C:/Users/mg/Documents/DataA/Final/FitabaseData/dailyActivity_merged.csv")
```
### Preview
```{r preview}
colnames(dailyActivity)
glimpse(dailyActivity)
head(dailyActivity)
```
### Clean Names
Cleaning names and assigning to the variable so changes apply
```{r clean names}
dailyActivity <- clean_names(dailyActivity)
```
### Summarizing Data with mean and arrange
```{r summarizing}
dailyActivity_mean_data <- 
  dailyActivity %>% 
    group_by(id) %>% 
    drop_na() %>% 
    summarise(mean_total_steps = mean(total_steps), 
              mean_total_distance = mean(total_distance), 
              mean_calories = mean(calories)) %>% 
    arrange(-mean_calories)
```
### Preview new data
```{r print mean_data}
print(dailyActivity_mean_data)
```
## Looking for the variable that best correlates with calories
### Summarizing Data with sum and arrange
Total steps and distance vs. calories
```{r total}
dailyActivity_total <- 
  dailyActivity %>% 
    group_by(id) %>% 
    drop_na() %>% 
    summarise(sum_total_steps = sum(total_steps), 
              sum_total_distance = sum(total_distance), 
              sum_calories = sum(calories)) %>% 
    arrange(-sum_calories)
```
### Preview total data
```{r print total}
print(dailyActivity_total)
```
### Correlating Intensity with totals
Total active, moderate and light activity distance vs. calories
```{r intensity totals}
intensity_total <- 
  dailyActivity %>% 
    group_by(id) %>% 
    drop_na() %>% 
    summarise(total_very_active_distance = sum(very_active_distance), 
              total_moderately_active_distance = sum(moderately_active_distance),
              total_light_active_distance = sum(light_active_distance),
              total_calories = sum(calories)) %>% 
  arrange(-total_calories)
```
### Preview intensity data
```{r print intensity total}
print(intensity_total)
```
### Searching for the correlation between intensity and calories
Mean active, moderate and light activity distance vs. calories
```{r intensity}
intensity_mean_data <- 
  dailyActivity %>% 
    group_by(id) %>% 
    drop_na() %>% 
    summarise(mean_very_active_distance = mean(very_active_distance), 
              mean_moderately_active_distance = mean(moderately_active_distance),
              mean_light_active_distance = mean(light_active_distance),
              mean_calories = mean(calories)) %>% 
  arrange(-mean_calories)
```
### Preview intensity data
```{r print intensity}
print(intensity_mean_data)
```
### Correlating intensity minutes and Calories
Total active, moderate and light activity minutes vs. calories
```{r minutes total}
intensity_minutes_total <- 
  dailyActivity %>% 
    group_by(id) %>% 
    drop_na() %>% 
    summarise(total_very_active_minutes = sum(very_active_minutes), 
              total_moderately_active_minutes = sum(fairly_active_minutes),
              total_light_active_minutes = sum(lightly_active_minutes),
              total_calories = sum(calories)) %>% 
  arrange(-total_calories)
```
### Preview minutes data
```{r print minutes total}
print(intensity_total)
```
## The Variables that best correlate with Calories
### Total Distance, Very Active Minutes and Light Active Distance
```{r vizualizations of correlations}
ggplot(dailyActivity_total, aes(x=sum_total_distance, y=sum_calories)) +
  geom_smooth(method = "lm", se= FALSE) +
  geom_point() +
  stat_poly_eq(use_label(c("eq", "R2")))

ggplot(intensity_total, aes(x=total_light_active_distance, y=total_calories)) +
  geom_smooth(method = "lm", se= FALSE) +
  geom_point() +
  stat_poly_eq(use_label(c("eq", "R2")))

ggplot(intensity_minutes_total, aes(x=total_very_active_minutes, y=total_calories)) +
  geom_smooth(method = "lm", se= FALSE) +
  geom_point() +
  stat_poly_eq(use_label(c("eq", "R2")))
```

